Refinements for open automata

### 2022-02-02 2021-Refinement/paper/refinementarticle.tex
corrections debut preuve thm2

\section{Proof of Context Refinement}
Let us denote by $A_{13}$ (resp. $A_{23}$) the open automaton resulting from $A_1\subst{A_3}{k}$ ($A_2\subst{A_3}{k}$),  to prove the theorem it sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}. The proof requires to resort to rename the elements (states, variables, etc) of an automaton according to the one to which they belong.

Let $R$ be the refinement relation relating states of $A_1$ and $A_2$. Let us consider any two states $s_{13} = \mpar{s_1,s^1_3}$ and $s_{23} = \mpar{s_2,s^2_3}$ ($s^1_3$ and $s^2_3$  are the same with renaming). We define a relation $R'$ relating states of $A_{13}$ and $A_{23}$ as follows:
\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in \fvars{s_{3}}
}\!\!\! v^1_3=v^2_3\wedge s^1_3 = s^2_3\]

We want to prove that $\mpar{R', H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$. In the following we denote $H'=H\cup J_3 \setminus\{k\}$
\begin{enumerate}
\item First, we have to prove:
\[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]

By using the fact that $R$ relates initial configurations of  $A_1$ and $A_2$, we have  the following statement holds:
$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$.
And secondly, because the domain of the substitution function is disjoint from the others, it has an effect only on the related elements, and relying on the  fact that initial states are reachable we  have:\TODO{define states and assignments}
\begin{align*}
& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge\underbrace{  \bigwedge_\subbox{v_3\in V_3} \sigma^1_{03}(v^1_3)=\sigma^2_{03}(v^2_3)\wedge s^1_3 = s^2_3}_{\Longleftrightarrow~\top?????}\\
\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{013} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
\implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
\end{align*}

@@

For all $x \in X$ we have to consider both  cases:
\begin{align*}
	\text{if } k \in J'_1:\quad &  J'_{23x} \cap H'  
=((J'_{2x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{3} ) \cap (H\uplus J_3 \setminus\{k\} )\\
&=((J'_{2x}\cap (H\uplus J_3))\uplus (J^{2 \prime}_{3}\cap (H\uplus J_3)))\setminus \mbrc{k}\\
&=((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}\cap  J_3))\setminus \mbrc{k}\text{ since } J_3\cap J'_{2x} = \emptyset \text{ and } H\cap J^{2 \prime}_{3} = \emptyset\\
& =((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}))\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
& =(J'_1\cap H)\uplus (J^{1 \prime}_{3})\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
& \text{faire reapparaitre J3 comme on l a elimine au dessus}\\
		& = \mpar{ J'_1  \uplus J^{1 \prime}_{3}\setminus \mbrc{k}} \cap \mpar{J_{3} \uplus H \setminus \mbrc{k}}\\
		& = J'_{13} \cap H'\\
\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = \mpar{J'_{2x} } \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
& = \mpar{J'_1\cap H }\\
& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'\\
\end{align*}

>>>>

\section{Proof of Context Refinement}

\proof
Let us denote by $A_{13}$ (resp. $A_{23}$) the open automaton resulting from $A_1\subst{A_3}{k}$ ($A_2\subst{A_3}{k}$),  to prove the theorem it sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}. The proof requires to resort to rename the elements (states, variables, etc) of an automaton according to the one to which they belong.

Let $R$ be the refinement relation relating states of $A_1$ and $A_2$. 
Let us denote with $t^1$ and $t^2$  the elements of $A_1$ and $A_2$ respectively.
Consider any two states $s_{13} = \mpar{s_1,s^1_3}$ and $s_{23} = \mpar{s_2,s^2_3}$ ($s^1_3$ and $s^2_3$  are the same with renaming). We define a relation $R'$ relating states of $s_{13}$ and $s_{23}$ as follows:
\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in \fvars{s_{3}}
}\!\!\! v^1_3=v^2_3\wedge s^1_3 = s^2_3\]

We want to prove that $\mpar{R', H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$. In the following we denote $H'=H\cup J_3 \setminus\{k\}$
\begin{enumerate}
\item First, we have to prove the following:
\[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]
with $\sigma_{013} = \sigma_{01} \uplus \sigma_{03}^1$ and $\sigma_{023} = \sigma_{02} \uplus \sigma_{03}^2$.\\
By using the fact that $R$ relates initial configurations of  $A_1$ and $A_2$, we have  the following statement:
$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$,  and relying on the  fact that initial states are reachable $\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ we have 
\[ \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\]
Composing with a tautology ${\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}$  and considering that  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
\begin{align*}
& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}}  \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3\\
\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{013} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
\implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
\end{align*}

@@

For all $x \in X$ we have to consider both  cases:
\begin{align*}
	\text{if } k \in J'_1:\quad &  J'_{23x} \cap H'  
=((J'_{2x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{3} ) \cap (H\uplus J_3 \setminus\{k\} )\\
&=((J'_{2x}\cap (H\uplus J_3))\uplus (J^{2 \prime}_{3}\cap (H\uplus J_3)))\setminus \mbrc{k}\\
&=((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}\cap  J_3))\setminus \mbrc{k}\text{ since } J_3\cap J'_{2x} = \emptyset \text{ and } H\cap J^{2 \prime}_{3} = \emptyset\\
& =((J'_{2x}\cap H)\uplus J^{2 \prime}_{3})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
& =(J'_1\cap H)\uplus J^{1 \prime}_{3}\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
&= ((J'_1 \cap H) \uplus (J^{1 \prime}_{3} \cap J_3)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{3}\subseteq J_3\\ 
& = (J'_1\cap (J_3 \uplus H)) \uplus ((J^{1 \prime}_{3} \cap (J_3 \uplus H)) \setminus \mbrc{k} \text{ since } J_3\cap J'_{1} = \emptyset \text{ and } H\cap J^{1 \prime}_{3} = \emptyset\\
		& = \mpar{(J'_1  \uplus J^{1 \prime}_{3})\setminus \mbrc{k}} \cap \mpar{(J_{3} \uplus H) \setminus \mbrc{k}}\\
		& = J'_{13} \cap H'\\
\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = \mpar{J'_{2x} } \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
& = \mpar{J'_1\cap H }\\
& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'\\
\end{align*}
